dispRity manual

### 2018-04-17 inst/gitbook/02_getting-started.Rmd
updated gitbook compiler with added cleaning

> This functionality is not available on the CRAN version of the package (1.0.3)<!-- versiontagCRAN --> due to CRAN compatibility issues see [to CRAN or not to CRAN?](#noCRAN) for more information and on how to install the GitHub (more complete) version of the package (1.1)<!-- versiontagGH -->.

>>>>

> This functionality is not available on the CRAN version of the package (`r version_CRAN`) due to CRAN compatibility issues see [to CRAN or not to CRAN?](#noCRAN) for more information and on how to install the GitHub (more complete) version of the package (`r version_release`).

### 2018-04-17 inst/gitbook/index.Rmd
updated gitbook compiler with added cleaning

@@

This is a package for measuring disparity in `R`.
It allows users to summarise matrices as representations as multidimensional spaces into a single value or distribution describing a specific aspect of this multidimensional space (the disparity).
Multidimensional spaces can be ordinated matrices from MDS, PCA, PCO, PCoA but the package is *not* restricted to any type of matrices!
This manual is based on the version `1.0.0`.

@@

Note this uses the `release` branch (1.1)<!-- versiontagGH -->.
For the piping-hot (but potentially unstable) version, you can change the argument `ref = release` to `ref = master`.
`dispRity` depends mainly on the `ape` package and uses functions from several other packages (`ade4`, `geometry`, `grDevices`, `hypervolume`, `paleotree`, `snow`, `Claddis`, `geomorph` and `RCurl`).

@@

Functions not available on the CRAN version (1.0.3)<!-- versiontagCRAN -->:

>>>>

```{r, eval = TRUE, echo = FALSE}
## master version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/master/DESCRIPTION")
version_master <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]

## release version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/release/DESCRIPTION")
version_release <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]

## CRAN version
version_raw <- RCurl::getURL("https://cran.r-project.org/web/packages/dispRity/index.html")
version_CRAN <- strsplit(strsplit(version_raw, split = "\n<td>Version:</td>\n<td>")[[1]][2], split = "</td>\n</tr>\n<tr>\n<td>Depends:")[[1]][1]
```

@@

This is a package for measuring disparity in `R`.
It allows users to summarise matrices as representations as multidimensional spaces into a single value or distribution describing a specific aspect of this multidimensional space (the disparity).
Multidimensional spaces can be ordinated matrices from MDS, PCA, PCO, PCoA but the package is *not* restricted to any type of matrices!
This manual is based on the version `r version_release`.

@@

Note this uses the `release` branch (`r version_release`).
For the piping-hot (but potentially unstable) version, you can change the argument `ref = release` to `ref = master`.
`dispRity` depends mainly on the `ape` package and uses functions from several other packages (`ade4`, `geometry`, `grDevices`, `hypervolume`, `paleotree`, `snow`, `Claddis`, `geomorph` and `RCurl`).

@@

Functions not available on the CRAN version (`r version_CRAN`):
